%1
\bibitem{deniz}
Deniz, P. S. R., Adaptive Filtering Algorithms and Practical Implementation,  2008, Third Ed., LLC, NY, Springer.

\bibitem{Haykins}
Haykin, S., Adaptive Filter Theory, 2002, Prentice Hall, Upper Saddle River, NJ.

%
\bibitem{Hayes}
Hayes, M. H., Statistical Digital Signal Processing and Modeling, 1996, John Wiley \& Sons. Inc., New York.

\bibitem{son}
%3
Sondhi, M. M., The History of Echo Cancellation, IEEE Signal Processing Magazine,  2006, 23, 95-102.

%4
\bibitem{Gay}
Gay, S. L., An Efficient Fast Converging Adaptive Filter for Network Echo Cancellation, Presented at the Thirty-Second Asilomar Conference on Signal, System and Amplifier, California, USA, November 1998, 394-398.

\bibitem{Gilloire}
Gilloire, A., Experiments with Sub-Band Acoustic Echo Cancellers for Teleconferencing, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP1987), April 1987, 2141-2144.

% 5
\bibitem{Duttweiler}
Duttweiler, D. L., Proportionate Normalised Least Mean Square Adaptation in Echo Cancelers, IEEE Transactions on Speech and Audio Processing,2000, 5, 508-518.

%
\bibitem{Romesburg}
Romesburg, E. D., Echo Canceller for Non-Linear Circuits, U.S. Patent, 5, August 1998, 796-819.


\bibitem{Benesty2}
Benesty, J., Gansler, T., Morgan, D. R., Sondhi, M. M., Gay, S. L., Advances in Network and Acoustic Echo Cancellation. Berlin, Germany: Springer-Verlag, 2001. DOI: 10.1007/978-3-662-04437-7.

\bibitem{Brookes}
Naylor, P. A., Cui, J., Brookes, M., Adaptive Algorithms for Sparse Echo Cancellation. Signal Processing, June 2006, 6, 1182-1192.



%6
 \bibitem{shukur}
 Salman, M. S., Kukrer, O., Hocanin, A., Adaptive Filtering Fundamentals and Applications, 2011, LAP LMBERT, U.S.A.

 %7
\bibitem{sayed}
Sayed, A. H., Adaptive Filters, 2008, John Wiley, Hoboken, New Jersey, 163-167.

%8
\bibitem{bellanger}
Bellanger, M. G., Adaptive Digital Filters, 2001, Second Ed., Marcel Dekker, New York.

%
\bibitem{Mathews}
Mathews, V. J., Zhenhua X., Stochastic Gradient Adaptive Filters with Gradient Adaptive Step-Sizes, International Conference on Acoustics, Speech, and Signal Processing (ICASSP1990), April 1990, 1385-1388.

\bibitem{Glover}
Widrow, B., Glover, J. R., McCool, J. M., Kaunitz, J., Williams, C. S., Hearn, R. H., Zeidler, J. R., Eugene Dong, Jr., Goodlin, R. C., Adaptive Noise Cancelling: Principles and Applications, Proceedings of the IEEE, December 1975, 1692-1716.


%15
\bibitem{Li}
 Li, Y., Gu, Y., Tang, K., Parallel NLMS Filters with Stochastic Active Taps and Step-Sizes for Sparse System Identiﬁcation, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP2006), May 2006, 3.
 
 %
\bibitem{Chitre}
Pelekanakis, K., Chitre, M., Comparison of Sparse Adaptive Filters for Underwater Acoustic Channel Equalization/Estimation, IEEE International Conference on Communication Systems (ICCS2010), November 2010, 17, 395-399.

%35
\bibitem{gui1}
Gui, G., Peng, W., Adachi, F., Improved Adaptive Sparse Channel Estimation Based on the Least Mean Square Algorithm, IEEE Wireless Communications and Networking  Conference (WCNC), Shanghai, China, April 2013, 3105-3109.

\bibitem{Douglas}
Gay, S. L., Douglas, S. C., Normalized Natural Gradient Adaptive Filtering for Sparse and Non-Sparse Systems, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP2002), Orlando, Florida, March 2002, 2, 1405-1408.

\bibitem{Hero}
Chen, Y., Gu, Y., Hero, A. O., Sparse LMS for System Identification, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP2009), Taipei, Taiwan, April 2009, 3125-3128.

\bibitem{Qing}
Jin, J., Qing, Q., Yuantao, G., Robust Zero-Point Attraction LMS Algorithm on Near Sparse System Identification, IET Signal Processing, 2013, 3, 210-218.

\bibitem{Gu1}
Gu, Y., Jin, J., Mei, S., $l_0$-Norm Constraint LMS for Sparse System Identification, IEEE Signal Processing Letters, 1985, 9, 774-777.

\bibitem{Christina}
Christina, B., Control of a Hands-Free Telephone Set, Signal Processing, ScienceDirect, 1997, 61, 131-143.

%
\bibitem{Elko}
Elko, G. W., Diethorn, E., Gansler, T., Room Impulse Response Variation Due to Thermal Fluctuation and its Impact on Acoustic Echo Cancellation, International Workshop on Acoustic Echo Noise Control (IWAENC2003), Kyoto, Japan, September 2003, 67-70.
%
\bibitem{Peterson}
Peterson, P. M., Simulating the Response of Multiple Microphones to a Single Acoustic Source in a Reverberant Room, Journal Of the Acoustical Society of America, Nov. 1986, 5, 1527-1529.

\bibitem{Dohono}
Donoho, D. L., Compressed Sensing, IEEE Transactions on Speech and Audio Processing, 2006, 4, 1289-1306.

\bibitem{Widrow}
Widrow, B., Stearn, S. D., Adaptive Signal Processing, 1985, Printice Hall, New Jersey.





%
\bibitem{Mandic}
Mandic, D. P., A Generalized Normalized Gradient Descent Algorithm, IEEE Signal Process Letters, February 2004, 11, 115-118.

% DOI: 10.1016/S0165-1684(97)00098-4

\bibitem{Etter1}
Cheng Y. F., Etter, D. M., Analysis of an Adaptive Technique for Modeling Sparse Systems, IEEE Transaction on Acoustics, Speech, and Signal
Processing, February 1989, 2, 254-264.



\bibitem{Candes2}
Candes, E. J., Wakin, M., An Introduction To Compressive Sampling, IEEE Signal Processing Magazine, March 2008, 2, 21-30.

%13
\bibitem{Salman}
Salman, M. S., Sparse Leaky-LMS Algorithm for System Identification and its Convergence Analysis, International Journal of Adaptive Control and Signal Processing, 2008, DOI:10.1002/acs. 2428.

\bibitem{Rey}
Rey, V. L., Rey, H., Benesty, J., Tressens, S., A Family of Robust Algorithms Exploiting Sparsity in Adaptive Filters, IEEE Transactions on Audio, Speech, and Language Processing, May 2009, 4, 572-581.

%14
\bibitem{Etter}
Etter, D. M., Identification of Sparse Impulse Response System Using an Adaptive Delay Filter, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP1985), April 1985, 10, 1169-1172.
%DOI: 10.1109/ICASSP.1985.1168275




%16
\bibitem{Xiang}
Khong, A. W. H., Xiang, L., Doroslovacki, M., Naylor, P. A., Frequency Domain Selective Tap Adaptive Algorithm for Sparse System Identification, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP2008), Las Vegas, Nevada, March 2008, 229-232.
%DOI: 10.1109/ICASSP.2008.4517588

%17
\bibitem{Kawamuri}
Kawamuri, S., Hatori,  M., A Tap Selection Algorithm for Adaptive Filters, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP1986), April 1986, 11, 2979-2982.
% DOI: 10.1109/ICASSP.1986.1168762

%18
\bibitem{Gu2}
Su, G., Jin, J., Gu, Y., Wang, J., Performance Analysis of $l_0$-Norm Constraint Least  Mean Square Algorithm, IEEE Transactions on Signal Processing, 2011, 6, 2223-2235.

%19
\bibitem{Jin}
Gu, Y., Jin, J., Mei, S., 2010. A Stochastic Gradient Approach on Compressive Sensing Signal Reconstruction Based on Adaptive Filtering Framework, IEEE Journal of Selected Topics in Signal Processing, 2011, 2, 409-420.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%20
\bibitem{Shi}
Shi, K., Shi, P., Convergence Analysis of Sparse LMS Algorithms with $l_1$-norm Penalty Based on White Input Signal, Signal Image and Video Processing, Springer, May 2010, 12, 3289-3293.

\bibitem{Slavakis}
Slavakis, K., Kopsinis, Y., Theodoridis, S., Adaptive Algorithm for Sparse System Identification Using Projections onto Weighted $l_1$-Balls, IEEE International Conference on Acoustics Speech and Signal Processing (ICASSP2012), March 2010, 3742-3745.


%21
\bibitem{Tong}
Wu, F. Y., Tong, F., Non-Uniform Norm Constraint LMS Algorithm for Sparse System Identification, IEEE Communications Letters 2013, 2, 385-388.

%
\bibitem{Johnson}
Martin, R. K., Sethares, W. A., Williamson, R. C., Johnson, C. R., Exploiting Sparsity in Adaptive Filters, IEEE Transactions on Signal Processing, August 2002, 8, 1883-1894.



%22
\bibitem{Harris}
Harris, R. W., Chabries  D. M., Bishop, F. A., A Variable Step (VS) Adaptive Filter Algorithm, IEEE Transactions on Acoustics, Speech and Signal Processing 1986, 2, 309-316.




%23
\bibitem{Kwong}
Kwong, R. H., Johnson, E. W., A Variable Step-Size LMS Algorithm,  IEEE Transactions on Signal Processing,1992, 7, 1633-1642.


%24
\bibitem{Brown}
Cui, J., Naylor, P. A. Brown, D. T., An Improved PNLMS Algorithm for Echo Cancellation in Packet-Switched Networks, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP2004), Toulouse, France, 3, May 2004, 141-144.

%25
\bibitem{Deng}
Deng, H., Doroslovacki, M., Improving Convergence of the PNLMS Algorithm for Sparse Impulse Response Identiﬁcation, IEEE Signal Processing Letters,2005, 3, 181-184.

%26
\bibitem{Morgan}
Benesty, J., Morgan, D. R., Sondhi, M. M., A Better Understanding and an Improved Solution to the Speciﬁc Problems of Stereophonic Acoustic Echo
 Cancellation, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP1998), 2, 156-165.

%27

%28
\bibitem{Shukri}
Salman, M. S., Jahromi, N., Hocanin, A., Kukrer, O., A Zero-Attracting Variable Step-Size LMS Algorithm for Sparse System Identification, IX International Symposium on Telecommunications (BIHTEL2012), Sarajevo, Bosnia and Herzegovina, October 2012, 1-4.
%DOI: 10.1109/BIHTEL.2012.6412087

%29
\bibitem{chart}
Chartrand, R., Exact Reconstruction of Sparse Signals Via Non-Convex Minimization, IEEE Signal Processing Letters, 2007, 10, 707-710.

%30
\bibitem{rao}
Rao, B. D., Delgado, K. K., An Affine Scaling Methodology for Best Basis Selection, IEEE Transaction on Signal Processing, January 1999, 1, 187-200.


%
\bibitem{Song3}
Rao, B. D., Bongyong S., Adaptive Filtering Algorithms for Promoting Sparsity, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP2003), June 2003, 6, 361-364.

%31
\bibitem{mujay}
Aliyu, M. L., Alkassim, M. A., Salman, M.S., A $p$-Norm Variable Step-Size LMS Algorithm for Sparse System Identification, Signal Image and Video Processing, Springer, DOI: 10.1007/s11760-013-0610-7.

\bibitem{mujay1}
Gwadabe T. R., Aliyu M. L., Alkassim, M.A., Salman M. S., Haddad H., A New Sparse Leaky LMS Type Algorithm. IEEE 22nd Signal Processing and Communications Applications Conference (SIU 2014), Trabzon, Turkey, April 2014.

%32
\bibitem{Loganathan}
Loganathan P., Sparseness-Controlled Adaptive Algorithms for Supervised and Unsupervised System Identification, Ph.D. Thesis, 2011, Imperial College, London.



%DOI: 10.1109/WCNC.2013.6555058

%36
\bibitem{gui2}
Gui, G., Adachi, F., Improved Adaptive Sparse Channel Estimation Using Least Mean Square Algorithm, EURASIP Journal on Wireless Communications and Networking, March 2013, 1, 1-18.


\bibitem{kennedy}
Kenney, J.F., Keeping, E.S., In Mathematics of Statistics, 1962, Third Ed. Van Nostrand, Princeton.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\\\\\\\\\\\\\\\\\\\\\\\\%%%%%%%%%%%%%%%%%%%%%%
%
\bibitem{Evans}
Evans, J. B., Xue p., Liu, B., Analysis and Implementation of Variable Step-Size Adaptive Algorithms, IEEE Transaction on Signal Processing, 8, 2517-2535.
%doi: 10.1109/78.229885

%
\bibitem{Mader}
Mader, A., Puder, H., Schmidt, G. U., Step-Size Control for Acoustic Echo Cancellation Filters-An Overview. Signal Processing, September 2000, 9, 1697-1719.



%
\bibitem{Reddy}
Reddy, V. U., Shan, T. J., Kailath, T., Application of Modified Least-Squares Algorithms to Adaptive Echo Cancellation, IEEE International Conference on  Acoustic, Speech and Signal Processing (ICASSP1983), April 1983, 8, 53-56.
%doi: 10.1109/ICASSP.1983.1172024.




%
\bibitem{Mayyas}
Mayyas, K., Aboulnasr, T., Leaky LMS Algorithm: MSE Analysis for Gaussian Data, IEEE Transactions on Signal Processing, April 1997, 4, 927-934.

%
\bibitem{Candes1}
Candes, E. J., Wakin, M., Boyd. S., Enhancing Sparsity By Reweighted $l_1$-Minimization, Journal of Fourier Analysis and Applications, October 2008, 14, 877-905.
%


%
\bibitem{Claasen}
Claasen, T., Mecklenbrauker, W., Comparison of the Convergence of Two Algorithms for Adaptive FIR Digital Filters, IEEE Transactions on Acoustics, Speech and Signal Processing, 3, June 1981, 670-678.

%
\bibitem{Hill}
Hill, S.I., Williamson, R.C., Convergence of Exponentiated Gradient Algorithms, IEEE Transactions Signal Processing, Jun 2001, 6, 1208-1215.




































